---
title: "Chirp"
author: "Srini"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objectives

In this project, we try to visualize the **chirp** signal. Since this signal
varies in power based on the frequency, visualization in the frequency domain using 
the **fft** of the signal is recommended. 

In addition, for plotting, we will use the \textbf{ggplot2} library.

## Chirp

The utility chirp can generate a chirp signal of a specified chirpiness.

```
usage: chirp outputfilename [chirpiness=0.1 [amplitude=1.0 [startfreq=220 endfreq=220]]]
```


## Setup the environment
```{r}
library(dplyr)
library(ggplot2)
```
\newpage

## Basic chirp signal - time domain

Generate a simple chirp signal .

```{bash}
../../chirp/bin/chirp chirp.csv 0.1 1.0 20 40
```

## Time domain plot

```{r}
chirp<-read.csv("chirp.csv")
names(chirp)<-c("t","y")
ggplot(chirp,aes(x=t,y=y))+geom_point()
```

\newpage 

## Frequency Domain transition

```{r}
fdomain <- data.frame( f = seq( 0, nrow(chirp) - 1 ) / ( nrow(chirp) * diff( chirp$t[ 1:2 ] ) ) )
fdomain$mag <- Mod( fft( chirp$y ) )
ggplot(slice_head(fdomain,n=60),aes(x=f,y=mag))+geom_line()
```


