---
title: "spect"
author: "Srini"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Generate signal and its fft

This generates a sinusoid 4 Hz, 1 second, sampled 200 Hz.

```{bash}
../bin/spect sin
```

## Plot the signal freq analysis

```{r}
library(ggplot2)
library(dplyr)
signalfft<-read.csv("sin.csv",header=FALSE,sep=",")
names(signalfft)<-c("freq","rex","imx","mod","arg")
```

### Dominant frequencies


The top 5 frequencies are

```{r}
head(signalfft,5)
```

```{r}
dominant<-signalfft %>% slice_head(n=10)
ggplot(dominant,aes(x=freq,y=mod))+geom_bar(stat="identity")
```

## Reconstructed waveform

```{r}
signal<-read.csv("sin_re.csv",header=FALSE,sep=",")
names(signal) <- c("x","y")
ggplot(signal,aes(x=x,y=y))+geom_point(colour="red", size=5,show.legend=TRUE)+theme(legend.position = "bottom")
```

\newpage

## Square Wave

```{bash}
../bin/spectsq sq
```

In this case, we use a much lower sampling frequency. The impact of the lower number of component sinusoids on the accuracy of the synthesis results should be obvious.
```{r}
rm(signalfft)
rm(dominant)
rm(signal)
signalfft<-read.csv("sq.csv",header=FALSE,sep=",")
names(signalfft)<-c("freq","rex","imx","mod","arg")
dominant<-signalfft %>% slice_head(n=10)
barplot(dominant$mod,col="steelblue",names.arg=dominant$freq,xlab="Frequency")
signal<-read.csv("sq_re.csv",header=FALSE,sep=",")
names(signal) <- c("x","y")
signalorig<-read.csv("sq_orig.csv",header=FALSE,sep=",")
names(signalorig) <- c("x","y")
signal <- signal %>% mutate(yorig=signalorig$y)
```

## Original and Reconstructed signals

```{r}
ggplot(signal,aes(x=x,y=y))+
      geom_line(colour="red",linewidth=1)+
      geom_line(aes(y=yorig),color="blue",linewidth=1)+
      theme(legend.position = "bottom")
```


  


