---
title: "Sinusoid"
author: "Srini"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sinusoid

The utility sinusoid can generate a sinusoid of a specified frequency, amplitude and phase shift.

```
sinusoid outputfilename <freq> <amplitude> <phase>
```

```{bash}
../../sinusoid/bin/sinusoid sine_4_1.5.csv 4 1.5
```
The above command generated a sinusoid of frequency=4 and amplitude 1.5. The output is in the form of a csv file. Now let us load and analyze the data.


```{bash}
../../sinusoid/bin/sinusoid sine_2_1_1.csv 2 1 1
```
Another sinusoid - freq=2 amplitude=1 phase=1

## Setup the environment
```{r}
library(dplyr)
library(ggplot2)
```
\newpage

## Load the table of values and plot

```{r}
values_4_15<-read.csv("sine_4_1.5.csv")
names(values_4_15)<-c("x","y")
plot(values_4_15$x,values_4_15$y,xlab="x",ylab="y")
```
\newpage

## Plot the square of the value

Let us create a column with the square of the value and plot that.
```{r}
values_4_15 <-values_4_15 %>% mutate(ysq=y^2)
plot(values_4_15$x,values_4_15$ysq,xlab="x",ylab="y^2")
```

\newpage

## Some signal algebra

```{r}
values_2_1_1<-read.csv("sine_2_1_1.csv")
names(values_2_1_1)<-c("x","y")
values_4_15<-cbind(values_4_15,y_2=values_2_1_1$y)
values_4_15<- values_4_15 %>% mutate(y_sum=ysq+y_2)
plot(values_4_15$x,xlab="x",values_4_15$y_sum,ylab="y_sum")
```

