---
title: "Exponential Chirp"
author: "Srini"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objectives

In this project, we try to visualize the **echirp** - the exponential chirp signal.

In addition, for plotting, we will use the **ggplot2** and **plotly** libraries.

## Exponential Chirp

The utility echirp can generate an exponential chirp signal of a specified frequencies.

```
usage: echirp outputfilename [amplitude=1.0 [startfreq=220 endfreq=440]]
```


## Setup the environment
```{r}
library(dplyr)
library(ggplot2)
library(plotly)
```
\newpage

## Basic exponential chirp signal - time domain

Generate a simple echirp signal .

```{bash}
../../echirp/bin/echirp echirp.csv
```

## Time domain plot

```{r}
echirp<-read.csv("echirp.csv")
names(echirp)<-c("t","y")
ggplot(echirp,aes(x=t,y=y))+geom_line()
```

\newpage

## Frequency Domain

```{r}
fechirp <- data.frame( f = seq( 0, nrow(echirp) - 1 ) / ( nrow(echirp) * diff( echirp$t[ 1:2 ] ) ) )
fechirp$mag <- Mod( fft( echirp$y ) )
p<-ggplot(slice_head(fechirp,n=nrow(echirp)/2),aes(x=f,y=mag))+geom_line()
ggplotly(p)
```


